Proposition of a New Experiment to Better Understand the Relation Between Typicality and Prototypes

### 2022-05-11 paper.tex
Done classical FE techniques

			\subsubsection{Classic feature extraction techniques}\\

@@

					\item \textbf{Principal Component Analysis(PCA)}:

@@

					\item \textbf{Independent component analysis(ICA)}:

@@

			\noindent These were not the only techniques presented in the paper, but since some were more problem-specific (about handwritten character recognition)
			were excluded from the list. These excluded techniques can still be used, but may have worse results or may require some adaptation. 
			The techniques were: Fractal theory techniques, Shadow features of character, Sector approach for feature extraction, 
			Extraction of distance and angle features, Extraction of occupancy and end-point features, and Zernike moments.
			In another paper, written in 2013 by Tian \cite{3}, there are some other techniques cited that may result useful:

@@

			A more sophisticated technique than the ones listed before is shape analysis. Deformable shape analysis, in particular,

@@

\section{Conclusion}
\section{Possible Further Experiments}
%\subsection{Figures and Tables}
%\paragraph{Positioning Figures and Tables} Place figures and tables at the top and 
%bottom of columns. Avoid placing them in the middle of columns. Large 
%figures and tables may span across both columns. Figure captions should be 
%below the figures; table heads should appear above the tables. Insert 
%figures and tables after they are cited in the text. Use the abbreviation 
%``Fig.~\ref{fig}'', even at the beginning of a sentence.
%
%\begin{table}[htbp]
%\caption{Table Type Styles}
%\begin{center}
%\begin{tabular}{|c|c|c|c|}
%\hline
%\textbf{Table}&\multicolumn{3}{|c|}{\textbf{Table Column Head}} \\
%\cline{2-4} 
%\textbf{Head} & \textbf{\textit{Table column subhead}}& \textbf{\textit{Subhead}}& \textbf{\textit{Subhead}} \\
%\hline
%copy& More table copy$^{\mathrm{a}}$& &  \\
%\hline
%\multicolumn{4}{l}{$^{\mathrm{a}}$Sample of a Table footnote.}
%\end{tabular}
%\label{tab1}
%\end{center}
%\end{table}
%
%\begin{figure}[htbp]
%\centerline{\includegraphics{fig1.png}}
%\caption{Example of a figure caption.}
%\label{fig}
%\end{figure}
%
%Figure Labels: Use 8 point Times New Roman for Figure labels. Use words 
%rather than symbols or abbreviations when writing Figure axis labels to 
%avoid confusing the reader. As an example, write the quantity 
%``Magnetization'', or ``Magnetization, M'', not just ``M''. If including 
%units in the label, present them within parentheses. Do not label axes only 
%with units. In the example, write ``Magnetization (A/m)'' or ``Magnetization 
%\{A[m(1)]\}'', not just ``A/m''. Do not label axes with a ratio of 
%quantities and units. For example, write ``Temperature (K)'', not 
%``Temperature/K''.
-

@@

\bibitem{1} J. S. Owotogbe,T. S. Ibiyemi, and B. A. Adu, ``Edge Detection Techniques on Digital Images - A Review'', International Journal of Innovative Science and Research Technology, vol. 4, issue 11, Nov. 2019
\bibitem{2} Gaurav Kumar, Pradeep Kumar Bhatia, ``A Detailed Review of Feature Extraction in Image Processing Systems'', FourthInternational Conference on Advanced Computing \& Communication Technologies, DOI \url{https://doi.org/10.1109/ACCT.2014.7}, 2014
\bibitem{3} Dong Ping Tian, ``A Review on Image Feature Extraction and Representation Techniques'', International Journal of Multimedia and Ubiquitous Engineering, vol.8, pp. 385-396, July 2013
\bibitem{4} Pedro F. Felzenszwalb, ``Representation and Detection of Deformable Shapes'', IEEE Transactions on Pattern Analysis and Machine Intelligence, vol. 27, no. 2, pp. 208-220, Feb. 2005, doi: \url{https://doi.org/10.1109/TPAMI.2005.35}

%\bibitem{b1} J. S. Owotogbe,T. S. Ibiyemi, and B. A. Adu, ``Edge Detection Techniques on Digital Images - A Review'', International Journal of Innovative Science and Research Technology, vol. 4, pp. 11, Nov. 2019
%\bibitem{1} J. Clerk Maxwell, A Treatise on Electricity and Magnetism, 3rd ed., vol. 2. Oxford: Clarendon, 1892, pp.68--73.
%\bibitem{b3} I. S. Jacobs and C. P. Bean, ``Fine particles, thin films and exchange anisotropy,'' in Magnetism, vol. III, G. T. Rado and H. Suhl, Eds. New York: Academic, 1963, pp. 271--350.
%\bibitem{b4} K. Elissa, ``Title of paper if known,'' unpublished.
%\bibitem{b5} R. Nicole, ``Title of paper with only first word capitalized,'' J. Name Stand. Abbrev., in press.
%\bibitem{b6} Y. Yorozu, M. Hirano, K. Oka, and Y. Tagawa, ``Electron spectroscopy studies on magneto-optical media and plastic substrate interface,'' IEEE Transl. J. Magn. Japan, vol. 2, pp. 740--741, August 1987 [Digests 9th Annual Conf. Magnetics Japan, p. 301, 1982].
%\bibitem{b7} M. Young, The Technical Writer's Handbook. Mill Valley, CA: University Science, 1989.
\end{thebibliography}

\end{document}

>>>>

			\subsubsection{Classic feature extraction techniques}

@@

					\item \textbf{Principal Component Analysis (PCA)}:

@@

					\item \textbf{Independent component analysis (ICA)}:

@@

			\noindent These were not the only techniques presented in the paper, but since some were more problem-specific (about handwritten character recognition)
			were excluded from the list. These excluded techniques can still be used, but may have worse results or may require some adaptation. 
			The techniques were: Fractal theory techniques, Shadow features of character, Sector approach for feature extraction, 
			Extraction of distance and angle features, Extraction of occupancy and end-point features, and Zernike moments.\\
			In another paper, written in 2013 by Tian \cite{3}, there are some other techniques cited that may result useful:

@@

			A more sophisticated technique than the ones listed before is shape analysis. Deformable shape analysis, in particular, can be useful to extract features from an image.\\
			In 2005, Felzenszwalb wrote a paper that focuses on representation and detection of deformable shapes~\cite{5}. For the goal of the experiment proposed here, some deformable shape 
			detection techniques can be useful. \\
			The technique proposed strongly relies on the trinagulated polygon representation. This type of representation lets approximate every 2D shape without holes using a representation based on triangles. 
			%The resulting approximation is as precise as the user decides, meaning that it's very flexible for the representation of shapes. 
			%In particular, in the paper the triangulation was done with a technique called constrained Delaunay triangulation (CDT), because of its tight relation with the medial axis transform. 
			The author also make use of the properties of chordal graphs and k-trees.\\
			The technique described in this paper falls under the category of deformable template matching. One of the components of the method is the energy function, a function that associates a cost with every 
			possible transformation. The objective is to find the transformation with the lowest possible cost. This component is very flexible, since depending on the formulation of the energy function the costs 
			can be tuned even for individual triangles. Moreover, it is also possible to integrate learning techniques to learn deformation parameters.
			Since the possible non-rigid transformations of a template are numerous, this kind of techniques usually requires an initialization near to the correct solution, 
			although this is not required for the algorithm presented in this paper. 
			For the implementation of the algorithm itself, a techniques called nonserial dynamic programming was the key factor. In fact, using the order of perfect elimination (property of the every triangulated 
			simple polygon), the algorithm computes the optimal position of every vertex with respect to the other vertices. Once the algorithm solves for the last vertex, it can 
			update all the others as in typical dynamic programming and obtain the optimal location for every vertex.\\
			The learning of the parameters can be seen as looking for the location with the highest. The matching problem is then fed to a statistical framework that computes the configuration minimizing the 
			energy cost, which corresponds to the best template match.

@@

\section{Conclusion}
\section{Possible Further Experiments}

%\paragraph{Positioning Figures and Tables} Place figures and tables at the top and 
%bottom of columns. Avoid placing them in the middle of columns. Large 
%figures and tables may span across both columns. Figure captions should be 
%below the figures; table heads should appear above the tables. Insert 
%figures and tables after they are cited in the text. Use the abbreviation 
%``Fig.~\ref{fig}'', even at the beginning of a sentence.

%\begin{table}[htbp]
%\caption{Table Type Styles}
%\begin{center}
%\begin{tabular}{|c|c|c|c|}
%\hline
%\textbf{Table}&\multicolumn{3}{|c|}{\textbf{Table Column Head}} \\
%\cline{2-4} 
%\textbf{Head} & \textbf{\textit{Table column subhead}}& \textbf{\textit{Subhead}}& \textbf{\textit{Subhead}} \\
%\hline
%copy& More table copy$^{\mathrm{a}}$& &  \\
%\hline
%\multicolumn{4}{l}{$^{\mathrm{a}}$Sample of a Table footnote.}
%\end{tabular}
%\label{tab1}
%\end{center}
%\end{table}

%\begin{figure}[htbp]
%\centerline{\includegraphics{fig1.png}}
%\caption{Example of a figure caption.}
%\label{fig}
%\end{figure}

%\appendix

%\section{Chordal graphs and k-trees}

@@

\bibitem{1} J. S. Owotogbe,T. S. Ibiyemi, and B. A. Adu, ``Edge Detection Techniques on Digital Images - A Review'', International Journal of Innovative Science and Research Technology, vol. 4, issue 11, Nov. 2019
\bibitem{2} Gaurav Kumar, Pradeep Kumar Bhatia, ``A Detailed Review of Feature Extraction in Image Processing Systems'', FourthInternational Conference on Advanced Computing \& Communication Technologies, DOI \url{https://doi.org/10.1109/ACCT.2014.7}, 2014
\bibitem{3} Dong Ping Tian, ``A Review on Image Feature Extraction and Representation Techniques'', International Journal of Multimedia and Ubiquitous Engineering, vol.8, pp. 385-396, July 2013
\bibitem{4} Chiranji Lal Chowdhary, D.P.Acharjya, Segmentation and Feature Extraction in Medical Imaging: A Systematic Review, vol. 167, pp. 26-36, Sep. 2019, doi: \url{https://doi.org/10.1016/j.procs.2020.03.179}
\bibitem{5} Pedro F. Felzenszwalb, ``Representation and Detection of Deformable Shapes'', IEEE Transactions on Pattern Analysis and Machine Intelligence, vol. 27, no. 2, pp. 208-220, Feb. 2005, doi: \url{https://doi.org/10.1109/TPAMI.2005.35}

\end{thebibliography}
\end{document}
